% Experience Section
\cvsection{Work Experience}

\cventry[Inter-University Centre for Astronomy and Astrophysics (IUCAA), Pune, India]{satellite}{Software Engineer, SUIT Payload of Aditya-L1 Mission}{Jun 2023}{Present}

\cvdescitem{Designed and implemented the SUIT data processing pipeline, handling $100$ Gb of daily data and delivering science-ready products within $24$ hours.}
\cvdescitem{Developed the Quick Look Display (QLD) for real-time data quality assessment and the Sun Center Finder for ISRO's mission feedback, both deployed at ISRO.}
\cvdescitem{Designed and implemented the SUIT internal database and query system for efficient data management along with the SUIT website with automated outreach product uploads.}
\cvdescitem{Developed and automated the SUIT website for outreach product uploads.}
\cvdescitem{Led the science and calibration observation planning during the SUIT payload verification phase.}
\cvdescitem{Created the SUIT simulator to verify program sequences before execution.}
\cvdescitem{Oversee daily operations at the SUIT Payload Operation Center, including observation planning, server maintenance, and data storage management.}

% \cvdescpara{In-charge of the science and calibration observation planning during the SUIT payload verification phase and designed and implemented the SUIT data processing pipeline, handling $100$~Gb of daily data and delivering science-ready products within 24 hours. Developed the Quick Look Display (QLD) for real-time data quality assessment and the Sun Center Finder for ISRO's mission feedback, both of which were successfully deployed at ISRO. Designed and implemented the SUIT internal database and query system for efficient data management and automated the SUIT website for outreach product uploads. Created the SUIT simulator to verify program sequences before execution and currently oversee daily operations at the SUIT Payload Operation Center, including observation planning, server maintenance, and data storage management.}
\cvspacer % Adds space between entries

\cventry[Inter-University Centre for Astronomy and Astrophysics (IUCAA), Pune, India]{satellite}{AstroSat Support Executive, CZTI Payload of AstroSat Mission}{Feb 2023}{May 2023}
\cvdescitem{Developed an automated Gamma Ray Burst (GRB) detection algorithm using the Sum Threshold method (Paper in preparation).}
\cvdescitem{Conducted X-ray polarization analysis using CZTI data and maintained a comprehensive catalog.}
%
% \cvdescpara{Developed an automated Gamma Ray Burst (GRB) detection algorithm using the Sum Threshold method (paper in prep.) and also conducted X-ray polarization analysis using CZTI data and maintained a comprehensive catalog.}

\cvspacer % Adds space between entries

\cventry[Inter-University Centre for Astronomy and Astrophysics (IUCAA), Pune, India]{satellite}{Scientific Trainee, CZTI Payload of AstroSat mission}{Feb 2022}{Feb 2023}

\cvdescitem{Developed a pipeline wrapper script to execute all processing modules based on user requirements.}
\cvdescitem{Analyzed CZTI data and reported approximately $40$ GRBs to the GCN Circulars Archive (View on ADS).}
\cvdescitem{Investigated the detectability of GRBs with CZTI and presented findings at the AstroSat CZTI Workshop at IUCAA in September 2022.}
\cvdescitem{Maintained the CZTI GRB catalog and updated it on the website (link).}
\cvdescitem{Monitored instrument health, identified and disabled noisy pixels, and performed targeted GRB searches based on reports from other instruments.}
% \cvdescitem{Ensured the smooth operation and maintenance of software systems in the CZTI POC.}
%
% \cvdescpara{Developed a pipeline wrapper script to execute all processing modules based on user requirements. Analyzed CZTI data and reported approximately 40 GRBs to the GCN Circulars Archive (View on ADS). Investigated the detectability of GRBs with CZTI and presented findings at the AstroSat CZTI Workshop at IUCAA in September 2022. Maintained and updated the CZTI GRB catalog on the website (link). Monitored instrument health, identified and disabled noisy pixels, and performed targeted GRB searches based on reports from other instruments. Ensured the smooth operation and maintenance of software systems in the CZTI POC.}
\cvspacer % Adds space between entries
