% Research Experience Section
\cvsection{Research Experience}

\cvbigentry[Indian Institute of Science Education and Research (IISER), Bhopal]{book-open}{Masters Thesis - From Hydrodynamics to Astrophysics - A Numerical Study}{May 2019}{April 2020}{Guide: Dr. Ritam Mallick, Associate Professor, IISER Bhopal, India}
\cvdescpara{Developed an exact numerical solver for Euler's equations and studied standard hydrodynamic problems such as the SOD shock tube and Sedov-blast problems by creating simulation codes. Applied these hydrodynamic techniques to model a toy supernova case, analyzing variations in physical properties.}

\cvspacer % Adds space between entries

\cvbigentry[Indian Institute of Science Education and Research (IISER), Bhopal]{book-open}{Course Project - Simulating Oscillating Chemical Reaction}{Jan 2019}{April 2019}{Guide: Dr. Nirmal Ganguly, Assistant Professor, IISER Bhopal}
\cvdescpara{Simulated the Belousov-Zhabotinsky (BZ) reaction, one of the most well-known oscillating chemical reactions, using numerical techniques such as the Runge-Kutta method and Newton-Raphson technique. Analyzed the conditions leading to periodicity and chaotic behavior in the reaction.}

\cvspacer % Adds space between entries

\cvbigentry[Indian Institute of Science Education and Research (IISER), Bhopal]{book-open}{Reading Project - Introduction to Solid State Physics}{May 2017}{July 2017}{Guide: Dr. Surajit Saha, Assistant Professor, IISER Bhopal}
\cvdescpara{Gained foundational knowledge in solid-state physics through laboratory work and literature review.}
\cvspacer
